Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
appendix G

\vspace{1ex}\noindent
%\begin{table}\caption{\leftline{Mapping}}
	\begin{tabular}{p{3cm}p{9cm}}
		\hline\specialrule{0em}{1pt}{1pt}			
		(Presentation)							
		&								\\\specialrule{0em}{1pt}{1pt}		
		&$Sorts \& Constructors \translate$	declare-datatypes				\\\specialrule{0em}{1pt}{1pt}
		&$Other operators \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{1pt}{1pt}
		(Open Transition)							
		&								\\\specialrule{0em}{1pt}{1pt}
		&$\EEnv ~~\lhook\joinrel\longrightarrow$	declare-const		\\\specialrule{0em}{1pt}{1pt}
		&$Pred ~~\lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{1pt}{1pt}
		&$\texttt{FUN}(x_1,...,x_n)$	\TODO {Xudong, why ?}	\\\specialrule{0em}{1pt}{1pt}
		&$\texttt{pNet expression} ~~\lhook\joinrel\longrightarrow$ SMTLib expression	\\\specialrule{0em}{1pt}{1pt}
		&$assignments$  assert	\\\specialrule{0em}{1pt}{1pt}
		\specialrule{0em}{1pt}{1pt}\hline
	\end{tabular}
%\end{table}

@@

@@

\newpage
\begin{figure}[h]
$\begin{array}{r@{}l}
    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
           {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
\end{array}$
  \smallskip

@@

We build a larger system by composing several subsystems. In the example here, we use two Failure Monitoring modules as the subsystems.
To compose them, a new controller is added for managing the reset function of the whole system. 
No matter which module behaves an "ask" to call for reset, the controller take the request. Then all of the modules conduct the "reset".
So two more new transitions are added to the Timer to make the module can reset at any state.

There are 327 satisfiable results, out of totally 97920 results, of the example computed in 105384 milliseconds.

>>>>

\vspace{1ex}\noindent
%\begin{table}\caption{\leftline{Mapping}}
	\begin{tabular}{p{3cm}p{9cm}}
		\hline\specialrule{0em}{1pt}{1pt}			
		(Presentation)							
		&								\\\specialrule{0em}{1pt}{1pt}		
		&$Sorts \& Constructors \translate$	declare-datatypes				\\\specialrule{0em}{1pt}{1pt}
		&$Other operators \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{1pt}{1pt}
		(Open Transition)							
		&								\\\specialrule{0em}{1pt}{1pt}
		&$\EEnv ~~\lhook\joinrel\longrightarrow$	declare-const		\\\specialrule{0em}{1pt}{1pt}
		&$Pred ~~\lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{1pt}{1pt}
%		&$\texttt{FUN}(x_1,...,x_n)$	\TODO {Xudong, why ?}	\\\specialrule{0em}{1pt}{1pt}
		&$\texttt{pNet expression} ~~\lhook\joinrel\longrightarrow$ SMTLib expression	\\\specialrule{0em}{1pt}{1pt}
		&$assignments$  assert	\\\specialrule{0em}{1pt}{1pt}
		\specialrule{0em}{1pt}{1pt}\hline
	\end{tabular}
%\end{table}

@@

In Fig.~\ref{schema:ots} we display the same OTs in a more human friendly format (but manualy translated into latex).

\begin{figure}[h]
$\begin{array}{r@{}l}
    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
           {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
\end{array}$
  \smallskip

@@

@@

We build a larger system by composing several subsystems. In the
example here (Fig.~\ref{schema:scaleup}), we use two Failure
Monitoring modules. 
To compose them, a new controller is added for managing the reset
function of the whole system.  
No matter which module emits an "ask" to call for reset, the
controller take the request. Then all of the modules are synchronised
on the "reset". 
So two more new transitions are added to the Timer to ensure the
module can reset at any state.

There are 327 satisfiable results, out of totally 97920 results, of
the example computed in 105384 milliseconds (~1.45 minutes).
